Choose a License

### 2025-02-08 choose_license.qmd
Fix typos
Introduced in 9e90838

- __fonts:__ Copyleft licenses applied to fonts can be a special case:
  If a font is put under the license [CC\ BY-SA\ 4.0][cc-by-sa],
  any documents containing texts using that font will probably be derivative works
  and have to be put under the same license if shared.
  The [SIL Open Font License\ 1.1][ofl] is the _de facto_ standard license for fonts,
  requiring that derived fonts, if published, have to be put under the same license.
  It doesn't require attribution for usage (e.g., when embedded in a document),
  but forbids that the font is sold by itself.
  Selling the font is allowed, however, if it is bundled with other software.
- __templates and TeX packages:__ If a template or, for this purpose, a $\TeX$ package,
  is licensed under a copyleft license such as the (A)GPLv3,
  every work that is a derivative of it has to be put under the same license if shared.
  If a document contained source code covered by the (A)GPLv3,
  it depends on the individual case
  whether the same license needs to be applied to the document if shared.
- __database content:__ If the work produced from a database (the "output")
  is a derivative of the content in the database,
  the output is subject to the restrictions laid out in the license.
  For example, if geospatial data were to be licensed under [CC\ BY\ 4.0][cc-by],
  all maps produced from the data would likely need to fulfill
  this license's obligation for unrestricted access (its Anti-DRM provision)
  if shared [see @Poole2017].
  Similarly, following an example from @Matt2009,
  if one were to choose the copyleft license [CC\ BY-SA\ 4.0][cc-by-sa]
  for this purpose, any map that is a derivative of the data
  would also need to be licensed under [CC\ BY-SA\ 4.0][cc-by-sa]
  (or a compatible license) if shared.
  If the intention is to only have [derivative databases][osm-produced-work]
  under the same license, one might want to choose the [ODbL\ 1.0][odbl] for the database,
  as it was specifically designed not to apply to works produced from the data in the database.
  Otherwise [CC0\ 1.0][cc0] is an excellent choice for data.
- __works in the public domain__: If a work is already in the public domain,
  it should be marked using the [PDM 1.0][pdm],
  rather than applying a waiver such as the [CC0\ 1.0][cc0] (or another license).
:::
https://creativecommons.org/licenses/by/4.0/
[ofl]: https://openfontlicense.org/
[cc-by]: https://creativecommons.org/licenses/by/4.0/
[pdm]: https://creativecommons.org/publicdomain/mark/1.0/
[osm-produced-work]: https://osmfoundation.org/wiki/Licence/Community_Guidelines/Produced_Work_-_Guideline

>>>>

- __fonts:__ Copyleft licenses applied to fonts can be a special case:
  If a font is put under the license [CC\ BY-SA\ 4.0][cc-by-sa],
  any documents containing texts using that font will probably be derivative works
  and have to be put under the same license if shared.
  The [SIL Open Font License\ 1.1][ofl] is the _de facto_ standard license for fonts,
  requiring that derived fonts, if published, have to be put under the same license.
  It doesn't require attribution for usage (e.g., when embedded in a document),
  but forbids that the font is sold by itself.
  Selling the font is allowed, however, if it is bundled with other software.
- __templates and TeX packages:__ If a template or, for this purpose, a $\TeX$ package,
  is licensed under a copyleft license such as the (A)GPLv3,
  every work that is a derivative of it has to be put under the same license if shared.
  If a document contained source code covered by the (A)GPLv3,
  it depends on the individual case
  whether the same license needs to be applied to the document if shared.
- __database content:__ If the work produced from a database (the "output")
  is a derivative of the content in the database,
  the output is subject to the restrictions laid out in the license.
  For example, if geospatial data were to be licensed under [CC\ BY\ 4.0][cc-by],
  all maps produced from the data would likely need to fulfill
  this license's obligation for unrestricted access (its Anti-DRM provision)
  if shared [see @Poole2017].
  Similarly, following an example from @Matt2009,
  if one were to choose the copyleft license [CC\ BY-SA\ 4.0][cc-by-sa]
  for this purpose, any map that is a derivative of the data
  would also need to be licensed under [CC\ BY-SA\ 4.0][cc-by-sa]
  (or a compatible license) if shared.
  If the intention is to only have [derivative databases][osm-produced-work]
  under the same license, one might want to choose the [ODbL\ 1.0][odbl] for the database,
  as it was specifically designed not to apply to works produced from the data in the database.
  Otherwise [CC0\ 1.0][cc0] is an excellent choice for data.
- __works in the public domain__: If a work is already in the public domain,
  it should be marked using the [PDM 1.0][pdm],
  rather than applying a waiver such as the [CC0\ 1.0][cc0] (or another license).
:::

[ofl]: https://openfontlicense.org/
[cc-by]: https://creativecommons.org/licenses/by/4.0/
[pdm]: https://creativecommons.org/publicdomain/mark/1.0/
[osm-produced-work]: https://osmfoundation.org/wiki/Licence/Community_Guidelines/Produced_Work_-_Guideline
